Symbolic Abstract Data Type Inference

### 2015-10-25 draft.tex
Better overview.
Tried to clean up the f**king mess of the algorithm section.
Space.
Applied SIGPLAN formatting guidelines.

\documentclass[9pt,preprint,nocopyrightspace,natbib,authoryear]{sigplanconf}

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{listings}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\img}{img}
\DeclareMathOperator{\width}{width}
\DeclareMathOperator{\weight}{weight}
\DeclareMathOperator{\freq}{freq}

@@

\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country}
\copyrightyear{20yy}
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
\doi{nnnnnnn.nnnnnnn}

@@

\authorinfo{}{}{}

% \authorinfo{Michael Emmi}
%            {IMDEA Software Institute}
%            {michael.emmi@imdea.org}
% \authorinfo{Constantin Enea}
%            {Université Paris Diderot}
%            {cenea@univ-paris-diderot.fr}

@@

\input intro
\input motivation
\input histories
\input inference
\input patterns
\input formula
\input algorithm
\input matching
\input nature
\input discussion
\input related

% \appendix

@@

\input appendix

>>>>

\documentclass[9pt,natbib,authoryear]{sigplanconf}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{listings}
\usepackage[ruled]{algorithm2e}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\img}{img}
\DeclareMathOperator{\width}{width}
\DeclareMathOperator{\weight}{weight}
\DeclareMathOperator{\freq}{freq}

@@

% \conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country}
% \copyrightyear{20yy}
% \copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
% \doi{nnnnnnn.nnnnnnn}
\toappear{}

@@

\authorinfo{Michael Emmi}
           {IMDEA Software Institute, Spain}
           {michael.emmi@imdea.org}

\authorinfo{Constantin Enea}
           {Université Paris Diderot, France}
           {cenea@univ-paris-diderot.fr}

@@

\input intro
\input overview
\input histories
\input inference
\input patterns
\input formula
\input algorithm
\input matching
\input nature
\input discussion
\input related

\appendix
\input appendix

@@
